%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rishi Shah 
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------
\newcommand{\award}[4]{{\textbf{#1}, }{\textit{#2}, }{#3} \hfill{#4}\\}
\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.6in,top=0.45in,right=0.6in,bottom=0.45in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
  \name{\LARGE Zhiyi(Zoe) Pan} % Your name
\address{1929 Plymouth Rd, Apt 5033, Ann Arbor, MI, 48105} % Your address
%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary addess (optional)
\address{1(734)881-5522  \\ panzhiyi1917@gmail.com}
% Your phone number and email
\usepackage{lipsum} % for dummy text
\usepackage{enumitem}
\setlist[itemize]{noitemsep, topsep=0pt}
\newenvironment{myitemize}
{ \begin{itemize}
    \setlength{\itemsep}{0pt}
    \setlength{\parskip}{0pt}
    \setlength{\parsep}{0pt}     }
{ \end{itemize}                  } 

\newcommand{\rrsection}[5]{%  
 {\textbf{#1}, }{\textit{#2}, }{#3} \hfill {#4\\} {#5}

  }
\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf University of Michigan, Ann Arbor, MI} \hfill {Aug. 2019 - May. 2021} 
\\ Bachelor of Computer Science
\\ \textit{Selected Coursework}: Advanced Compilers; Program Synthesis; Introduction to Operating Systems; Compiler Construction; Programming Languages; 
 \hfill { GPA: 3.84}
%\\ Department of Structural Engineering\\
\\{\bf Shanghai Jiao Tong University, Shanghai} \hfill {Sept. 2017 - May. 2021} 
\\Bachelor of Electronic and Computer Engineering 
 \hfill { GPA: 3.55}
%Minor in Linguistics \smallskip \\
%Member of Eta Kappa Nu \\
%Member of Upsilon Pi Epsilon \\


\end{rSection}

\begin{rSection}{SKILLS}
\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Front-end skills: & Proficient in HTML/CSS/Javascript, Bootstrap; experience in jQuery, vue.js.\\
Back-end skills: & Proficient in C/C++, Python (Django); experience in PHP, nginx, uwsgi, Apache.  \\
Database skills: & Experience in MySQL.
\end{tabular}

\end{rSection}
%--------------------------------------------------------------------------------
%    Projects And Seminars
%-----------------------------------------------------------------------------------------------
  
\begin{rSection}{RESEARCH EXPERIENCE}
\begin{rrsection}{Research Assistant}{prof. Cyrus Omar}{University of Michigan - Future of Programming Lab}{ Nov. 2019 - present}
  \item Worked on a paper for a gradual bidirectional typing inference system - type hole inference. 
  \item Developed undo/redo and history recording features for Hazel, a live functional programming environment featuring typed holes.
  \item Designed and implemented a history panel, which was used for EECS 490 teaching work in UM. 
\end{rrsection}	
\begin{rrsection}{Research Assistant}{prof. Scott Mahlke}{University of Michigan}{ May 2020 - Jul. 2020}
\item Learnt and wrote optimization path by LLVM.
  \item Implemented genetic algorithm to find optimized combination of flags for gcc.
\end{rrsection}	
\end{rSection}
\begin{rSection}{ENGINEERING EXPERIENCE}

\begin{rrsection}{Course Project}{Compiler for Decaf}{EECS 483
  Compiler Construction}{2019 Winter}
  Implemented and optimized a compiler for Decaf (a strongly-typed, object-oriented language with support for inheritance and
encapsulation), written in C++ and compiled Decaf program into MIPS assembly program.
  \item Implemented a full-stack compiler from lexical analyzing to code generation with clear static, link and run-time error reporting.
  \item Optimized compiler by register allocation improvement, dead code elimination, constant folding, subexpression elimination, constant propagation and forward copy propagation.

\end{rrsection}

\begin{rrsection}{Course Project}{Network File System}{EECS 482
  Operating System}{2019 Winter}
  \item Implemented a file system featuring encryption, authentication, failure tolerance and concurrency.
\end{rrsection}

\begin{rrsection}{Lead Programmer}{Online Visual Novel}{SJTU Network and Information Organization}{February 2019 - May 2019}

	\item Implemented a visual novel featuring multiple story lines and endings, shopping store, archiving, achievement, HP systems.

  \item Designed and built front-end pages (Html/CSS/JS).
  \item Developed the back-end by Django, created database model and deployed it in the cloud server (Ubuntu).
  \item Revised it into a light framework and released on github.
\end{rrsection}

%\vspace{-0.3\baselineskip}


\end{rSection}
%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{ACADEMIC EXPERIENCE}

\begin{rrsection}{Instructional Aide (IA)}{EECS 490 Programming Languages}{University
  of Michigan}{2020 Fall}
  \item 250-student upper level technical elective course
  \item duties including holding office hours and lab teaching
\end{rrsection}

\begin{rrsection}{Author}{ICFP 2020}{Student Research Competition Track}{Aug. 2020}
  \item Won bronze medal in the student research competition.
  \item Submitted an extended abstract, \textit{Type Hole Inference}.
  \item Participated in the poster session and communicated with ICFPers.
  \item Made a presentation on the final talk session.
\end{rrsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Awards}   

\award{Bronze}{ICFP 2020}{Student Research Competition}{Aug. 2020}
\award{Champion}{12th Annual VEX U Robot Skills Challenge World Championship}{Louisville}{Apr. 2019}
Over 30,000 people including more than 1,650 teams from 40 nations participated.
\begin{itemize}
  \item Designed and constructed over 5 versions of robots for competitions with other 8 teammates. 
	\item Wrote daily work log and engineering sheets for the team.
 \end{itemize} 
\award{Second Place}{12th Annual VEX U Robot World Championship}{Louisville}{Apr. 2019}
\award{Champion}{VEX Robotics Asia Open}{Ningbo, Zhejiang}{Feb. 2019}
\award{Robot Awards}{Summer Design Expo Best Technology Award}{UM-SJTU JI}{Nov. 2018}
\award{Scholarship}{Undergraduate Excellent Scholarship}{Shanghai Jiao Tong University}{2017-2018}
\end{rSection}


%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------


\end{document}
